---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![Codecov test coverage](https://codecov.io/gh/msperlin/GetTDData/branch/master/graph/badge.svg)](https://app.codecov.io/gh/msperlin/GetTDData?branch=master)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

# Package `GetTDData`

Information regarding prices and yields of bonds issued by the Brazilian government can be downloaded from the official open data portal at [Tesouro Transparente](https://www.tesourotransparente.gov.br/ckan/dataset/taxas-dos-titulos-ofertados-pelo-tesouro-direto/). However, aggregating all of this historical data into a structured format can be challenging.

Package `GetTDData` makes importing data from Tesouro Direto simple and fast. All you need to download bond data is the asset identifier (LFT, LTN, NTN-C, NTN-B, NTN-B Principal, NTN-F, NTN-B1, Educa+, RendA+). Function `td_get2()` downloads directly from the official Tesouro Transparente CKAN open data repository.


## Installation

```
# from CRAN (stable version)
install.package('GetTDData')

# from github (development version)
devtools::install_github('msperlin/GetTDData')
```

## How to use GetTDData

Suppose you need financial data (prices and yields) for a bond of type LTN with a maturity (end of contract) at 2023-01-01. This bullet bond is the most basic debt contract the Brazilian government issues. It does not pay any coupon during its lifetime and pays R$ 1,000 at maturity.

In order to get the data, all you need to do is run the following code in R using `td_get2()`:

```{r example1}
library(GetTDData)

assets <- 'LTN'   # Identifier of assets 
first_year <- 2020
last_year <- 2022

df_td <- td_get2(assets,
                 first_year,
                 last_year)
```

Let's plot the prices to check if the code worked: 

```{r plot.prices, fig.width=7, fig.height=2.5}
library(ggplot2)
library(dplyr)

# filter  LTN 
my_asset_code <- "LTN 010123"

LTN <- df_td %>%
  filter(asset_code  ==  my_asset_code)

p <- ggplot(data = LTN, 
            aes(x = as.Date(ref_date), 
                y = price_bid, 
                color = asset_code)) + 
  geom_line(linewidth = 1) + scale_x_date() + labs(title = '', x = 'Dates')

print(p)
```


## Downloading the Brazilian Yield Curve

The latest version of `GetTDData` offers function `get_yield_curve` to download the current Brazilian yield curve directly from Anbima. The yield curve is a tool of financial analysts that show, based on current prices of fixed income instruments, how the market perceives the future real, nominal and inflation returns. You can find more details regarding the use and definition of a yield curve in [Investopedia][https://www.investopedia.com/terms/y/yieldcurve.asp].

```{r, eval=TRUE}
df_yield <- get_yield_curve()  
str(df_yield)
```

And we can plot it for the desired result:

```{r, eval=TRUE}
library(ggplot2)

p <- ggplot(df_yield, aes(x=ref_date, y = value) ) +
  geom_line(size=1) + geom_point() + facet_grid(~type, scales = 'free') + 
  labs(title = paste0('The current Brazilian Yield Curve '),
       subtitle = paste0('Date: ', df_yield$current_date[1]))     

print(p)
```
